Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-11-25 Scripts/Initial_Analysis.Rmd
Showing median in figure 3, not mean

```{r emergence_map_plot, eval = F}
# -------------------------- #
# Call plot for both tresholds
# -------------------------- #
tresh_list <- c("tresh_one","tresh_two")
i = 2
for(i in 2){

@@

  boxplot <- ggplot(boxplot_data) +
    geom_violin(
      aes(
        x = reorder(un_sub_region,order),
        y = emerging_yr
      ),
      fill = "grey"
    ) + 
    facet_wrap(~un_geo_region,
               scales = "free_x",
               nrow = 1) +
    # Median points
    geom_point(
      aes(
        x = reorder(un_sub_region,order),
        y = mean,
        colour = mean
      ),
      size = 5
    ) + 
    # h line
    geom_hline(yintercept = 2030, color = "grey", size = 0.5, linetype="dashed") +
    scale_colour_viridis("",
                         limits = c(2000,2100),
                         breaks = seq(2000,2100,25),
                         labels = c("","","","",""),
                         direction = -1
    ) +
    xlab("") +
    ylab("Year of range shift") +
    scale_y_continuous(
      labels = c(2000,2025, 2050, 2075, ">2100"), # not inluding the > because we dont know
    ) +
    my_ggtheme_p() +
    theme(
      axis.text.x = element_text(size = 16, angle = 45, face = "plain", hjust = 1), 
      strip.text.x = element_text(size = 18, colour = "black"), 
      axis.title.y = element_text(size = 18),
      axis.text.y = element_text(size = 16), 
      panel.background = element_rect(colour = "white", fill = "white"),
      # axis.ticks.x = element_blank(),
      legend.position = ""
    );boxplot

  ggsave("mean_boxplot.png",boxplot,width = 10)

>>>>

```{r emergence_map_plot, eval = F}
# -------------------------- #
# Call plot for both tresholds
# -------------------------- #
tresh_list <- c("tresh_one","tresh_two")

for(i in 1:2){

@@

  boxplot <- ggplot(boxplot_data) +
    geom_violin(
      aes(
        x = reorder(un_sub_region,order),
        y = emerging_yr
      ),
      fill = "grey"
    ) + 
    facet_wrap(~un_geo_region,
               scales = "free_x",
               nrow = 1) +
    # Median points
    geom_point(
      aes(
        x = reorder(un_sub_region,order),
        y = med,
        colour = med
      ),
      size = 5
    ) + 
    # h line
    geom_hline(yintercept = 2030, color = "grey", size = 0.5, linetype="dashed") +
    scale_colour_viridis("",
                         limits = c(2000,2100),
                         breaks = seq(2000,2100,25),
                         labels = c("","","","",""),
                         direction = -1
    ) +
    xlab("") +
    ylab("Year of range shift") +
    scale_y_continuous(
      labels = c(2000,2025, 2050, 2075, ">2100"), # not inluding the > because we dont know
    ) +
    my_ggtheme_p() +
    theme(
      axis.text.x = element_text(size = 16, angle = 45, face = "plain", hjust = 1), 
      strip.text.x = element_text(size = 18, colour = "black"), 
      axis.title.y = element_text(size = 18),
      axis.text.y = element_text(size = 16), 
      panel.background = element_rect(colour = "white", fill = "white"),
      # axis.ticks.x = element_blank(),
      legend.position = ""
    );boxplot

  # ggsave("mean_boxplot.png",boxplot,width = 10)
